\chapter{State of the Art}

  This chapter will review the classic methods used for localization and mapping, which is the core for any navigation technique, it starts describing the problems that arise both in localization and mapping. Continue with some of the most prolific solutions found to these problems to finish exposing the techniques and algorithms used by the Aerostack framework.

  Localization is referred to all the techniques used to find the position in coordinates of an agent or object inside the world, relative to a reference frame. As far as it's absolute coordinates are known, anything can be used as reference frame, it is used as the coordinates system's centre. In an outdoors environment, the Earth could be the reference frame and the robot's coordinates can be acquired with Satellite systems, giving an absolute point inside the three dimensional space. It is desirable for these coordinates to be in a way that a computer can handle efficiently, tipically as two or three floating point numbers (although integer numbers are used sometimes too), depending on the number of dimensions used to represent the space. To save computational effort, the y axis could be unused in a wheeled robot.

  Moving a robot avoiding possible obstacles through the space is tricky in itself, obstacles must be detected and handled correctly, moving objects can appear in the way, and so on. This alone does not provide any intelligence nor it helps planning, to aid in planning and moving smartly in the space, a map can be constructed while the localization is happening. The term mapping covers all the algorithms used to construct a map combining the data acquired from the many input sources a robot can have. Mapping opens the door for smart planning, along with many more advantages. A classic example is finding cycles in planned paths.

  \clearpage

  \section{Localization}

    Localization techniques are divided into two groups: Outdoor and indoor techniques. The distinction comes from the fact that Satellite systems signals cannot go through walls. This fact has led to a whole new set of technologies and techniques that are able to localize in environments without an absolute reference of the world.

    This section is organized as follows: First outdoor localization will be analyzed, with a brief review of it's core components, then various indoor localization techniques will be exposed, focusing on lidar based techniques.

    \subsection{Outdoor localization}

      By now, the most robust, reliable solution for outdoor localization is based on combining different sources of data. The mobile platform has drawn great attention over the past few years, pushing some of the largest companies in a shared effort to improve localization services while minimizing the impact over the battery's performance.

      Satellite systems localization in mobile applications have certain drawbacks: The most obvious one is that acquiring and processing the signal wastes power, but also that in the case of civilian systems (such as GPS) the localization has precision of 10 meters for security reasons. 

      To aid both problems two new localization techniques were implemented:
      \begin{enumerate}
        \item GSM Localization. As every GSM antenna has a well known location stored in a database, one can localize trilaterating the near GSM antennas. Obviosly, this method is subject to GSM signal coverage.
        \item WiFi Localization. This powerful method can serve both as an indoor and outdoor localization technique (see \ref{ch_4:sect:localization:indoor}). When a smarphone detects a wifi hotspot, it sends it's BSSID along with the GPS coordinates if available to a centralized server. As this database grows the localization precision improves and every user can take advantage from it. This is scpecially useful in urban areas where stallite signal is poor or intermitent and improves as more and more users log information.
      \end{enumerate}

      The best localization services can be provided with the conjunction of these three main techniques, which can be easily merged with an \textit{Extended Kalman Filter}.


      Although these techniques are widely used they are limited to mobile platforms, which are limited both in sensorization and in processing capabilities. For robotic applications more sophisticated sensors can be used, this includes 

    \subsection{Indoor localization}


  \begin{comment}
    Organization:
      - Localization and mapping: Talk about Localization techniques:
        - Outdoor: GPS
        - Indoor: Bluetooth/WiFi Beacons, OptiTrack camera, Image-Based algorithms
  \end{comment}

  \begin{comment}
    \begin{itemize}
    \end{itemize}
  \end{comment}
